\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2020-03-11 popl-2019-journal-v/paper.tex
Lars's ORCID
Update the acks section

\author{Lars Birkedal}
% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \institution{Aarhus~University}
  \country{Denmark}                    %% \country is recommended
}
\email{birkedal@cs.au.dk}

@@

\begin{acks}
  This research was supported in part by the ModuRes Sapere Aude
  Advanced Grant from The Danish Council for Independent Research for
  the Natural Sciences (FNU) and by Cost Action CA15123 EUTypes.
  Dominique Devriese held a Postdoctoral Fellowship from the Research Foundation - Flanders (FWO) during most of this research.
\end{acks}

>>>>

\author{Lars Birkedal}
\orcid{0000-0003-1320-0098}          %% \orcid is optional
\affiliation{
  \institution{Aarhus~University}
  \country{Denmark}                    %% \country is recommended
}
\email{birkedal@cs.au.dk}

@@

\begin{acks}
  This research was supported in part by the ModuRes Sapere Aude Advanced Grant
  from The Danish Council for Independent Research for the Natural Sciences (FNU).
  Support for an STSM was received from COST Action EUTypes (CA15123).
  Dominique Devriese held a Postdoctoral fellowship from the Research Foundation
  Flanders (FWO) during most of this research.
  This research was supported in part by the Research Foundation Flanders (FWO).
\end{acks}
